### 2017-11-27 monograph/thesis/chapters/introduction.tex
Created initial text for the section Related Works on
monograph/thesis/chapters/introduction.tex
Created some weblink references/footnotes.
Created notes about the work development on introduction.tex
Partially translated General Goals, moved to Research Goals the
Focused Goals section from object_beautifier.tex and translated the
Future Works section.

    \begin{enumerate}
        \item Establish relationships between good programming practices and efficiency in
              programming, in addition to a new tool to support programmers in order to
              automate the long and diverse programming process in teams of developers
              with different programming `best practices'.
        \item Define, determine and classify which one are good programming
              practices and perform an in-depth study on the good practices on visual
              layout area, also known as code `Beautifying'.
        \item The definition of a flow pattern of development allowing teams of
              developers with different programming best practices, to work without
              intervene with each other up to start wars of `best good practices'.
        \item Discourse on the variety of existing tools for the support of good
              programming practices, with a comparative analysis between them,
              determining their weaknesses and strengths.
    \end{enumerate}

@@

% 1.2      Rascunho da Monografia para TCC1

% 1.2.1    * Introdução       Uma breve descrição dos objetivos e da
%            justificativa para realização do projeto. Uma breve explicação de
%            qual a necessidade e importância deste projeto no escopo da
%            Ciência da Computação. Os objetivo gerais e específicos buscados
%            após a conclusão e análise deste projeto.

% 1.2.2    * Bibliográfia     Fazer uma análise do estado da arte em relação
%          ao que existe hoje em dia de cunho científico, comentando sobre os
%          diversos trabalhos na área de beautifying.

% 1.2.3    * Classificações   Escrever sobre quais são os tipos possíveis de
%          beautifying. Quais são as técnicas mais eficientes, para quais
%          linguagens ele se aplicam.

% Cronograma:

% Id      Atividade                               Data início    Data fim
% 1.2.2.a Escrever sobre os Formatadores Atuais   31/07/2017     30/08/2017
% 1.2.2.b Escrever sobre as Pesquisas Atuais      01/09/2017     15/09/2017
% 1.2.3.a Escrever as Classes de Beautifying      16/09/2017     30/09/2017
% 1.2.3.b Escrever os Tipos de Beautifying        01/10/2017     30/10/2017
% 1.2.4.a Fazer a Revisão do Texto Escrito        31/10/2017     20/11/2017

>>>>

    Beforehand due the scope limitation for a Graduation Thesis,
    we should only think about a basic, simple,
    and yet reusable core of features.

    \begin{enumerate}
        \item A Software Product with a great Object Orientation and possibilities of extension of features,
        decent research on the state of the art.

        \item Ranking all code formatting classes (beautifying) applicable.
        Including a study on what does is source beautifying,
        how to do such and why.

        \item Establish relationships between good programming practices and efficiency in programming,
        in addition to a new tool to support programmers in order to automate the long and diverse
        programming process in teams of developers with different programming `best practices'.

        \item Define, determine and classify which one are good programming practices and
        perform an in-depth study on the good practices on visual layout area,
        also known as code `Beautifying'.

        \item The definition of a flow pattern of development allowing teams of
        developers with different programming best practices,
        to work without intervene with each other up to start wars of `best good practices'.

        \item Discourse on the variety of existing tools for the support of good programming practices,
        with a comparative analysis between them,
        determining their weaknesses and strengths.
    \end{enumerate}

@@

% 1.2      Rascunho da Monografia para TCC1
%
% 1.2.1    * Introdução       Uma breve descrição dos objetivos e da
%            justificativa para realização do projeto. Uma breve explicação de
%            qual a necessidade e importância deste projeto no escopo da
%            Ciência da Computação. Os objetivo gerais e específicos buscados
%            após a conclusão e análise deste projeto.
%
% 1.2.2    * Bibliográfia     Fazer uma análise do estado da arte em relação
%          ao que existe hoje em dia de cunho científico, comentando sobre os
%          diversos trabalhos na área de beautifying.
%
% 1.2.3    * Classificações   Escrever sobre quais são os tipos possíveis de
%          beautifying. Quais são as técnicas mais eficientes, para quais
%          linguagens ele se aplicam.

% Cronograma:
%
% Id      Atividade                               Data início    Data fim
% 1.2.2.a Escrever sobre os Formatadores Atuais   31/07/2017     30/08/2017
% 1.2.2.b Escrever sobre as Pesquisas Atuais      01/09/2017     15/09/2017
% 1.2.3.a Escrever as Classes de Beautifying      16/09/2017     30/09/2017
% 1.2.3.b Escrever os Tipos de Beautifying        01/10/2017     30/10/2017
% 1.2.4.a Fazer a Revisão do Texto Escrito        31/10/2017     20/11/2017

% Coloca ChannelManager no tópico e boas praticas, e comenta sobre o modelo de
% fork e canais.
%
% Inclui a IA para reconhecer o formatação nos módulos de beautifying. Ela eh
% uma heurística, que cada bloco implementa e faz ele gerar um arquivo de
% configuração que representa a atual formatação do código (aqui esta o
% verdadeiro desafio do trabalho, pesquise trabalhos correlatos).
%
% Inclui sobre a implementação  do semantic linefeed implementado na seção do
% linefeed.
%
% Somente incluí somente o que é mais importante para entender o trabalho, não
% queira mostrar tudo o que você fez. Uma trabalho extensivo não é necessário,
% basta somente apontar como uma referencia que inclua o que você fez.
%
% Mas não esqueça de incluir como foi implementado, i.e., os diagramas UML, se
% o sistema é extensível, as bibliotecas utilizadas, como os testes foram
% feitos e os resultados deles.
%
% Coloca no capítulo de motivação a seção de trabalhos relacionados. Trabalhos
% relacionados com beautifying e com as boas práticas de programação (code clean,
% GOF, DEITEL (forminhas das boas práticas)). E deixa claro qual é o problema
% que se está resolvendo.
%
% Cria uma capitulo de comparação com os trabalhos relacionados, tanto a parte
% teórica (boas práticas), quanto a parte prática (beautifier). Complexidade do
% algoritmo do beautifier e o que esse trabalho tem de diferente dos outros.
%
% Coloque evidencias de que funciona o formatador, de boas práticas, mas
% práticas e críticas.
%
% Fazer um texto mais didático com exemplos, para os leitores leigos.

    \section{Related Works}

    The problem on Integration Tests to find which tests must to be re\hyp{}run
    after some code has been changed. There is no way of determine which
    tests must to re\hyp{}run after some code has changed without knowing the
    language syntax and semantics. TODO put reference to this

    \url{http://editorconfig.org/}

### 2017-11-27 monograph/thesis/chapters/object_beautifier.tex
Improved the beautifiers.tex For what is their use?' section
introduction.
Fixed wrong \label creations over the project files.
Partially translated General Goals, moved to Research Goals the
Focused Goals section from object_beautifier.tex and translated the
Future Works section.

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{Object Beautifier}

@@

        \item Write the program in C++ for greater performance, allowing the
        formating/beautifying to be dynamic, i.e., as you type the text, the
        text is formatted for you. So you can focus more on writing the code,
        rather than worrying about spacing, alignment, parentheses, new lines,
        and whatever else.

        Utilizar o Framework `doctest` para escrita dos Testes de Unidade. Pois após procurar e
        testar alguns frameworks para testes de unidade em C++, entrou-se este como servindo muito
        bem as requisitos do projecto. Ele causa baixíssimo incremento no tempo de compilação e
        permite que os testes possam ser escritos no mesmo arquivo onde encontram-se o código do
        programa, sem que eles sejam compilados.

        Utilizar uma versão/algoritmo multi-core, então cada uma das regras pode ser processada em
        paralelo e sobre o mesmo source code original. Essa parte é bastante complexa de ser escrita
        por que as regras entre si podem gerar conflitos sobre o que elas estão fazendo. Para
        resolver esse problema, fazer com que cada regra processada gere um objeto de mudanças que
        essa regra está propondo. No final do processamento de todas as regras, será realizado um
        fusão das mudanças que cada uma decidiu realizer, e caso duas regras queriam mudar o mesmo
        pedaço/trecho de código, será lançada um exceção e uma nova classe de mudanças/regra deve
        estar disponível para resolver esse conflito. Caso não exista, ambas as mudanças são
        descartadas e somente as mudanças sem conflitos são refletidas no código.

@@

\subsubsection{Focused Goals}

        Um Produto de Software com uma ótima orientação a objetos e possibilidades de extensão das
        funcionalidades.

        Classificar todas classes e tipos de formatações (beautifying) de código aplicáveis com
        facilidade. Uma das partes a serem escritas e entregues na monografia. Um estudo sobre o que
        é beautifying, como fazer e por que fazer.

        Implementação de um núcleo funcional e de uma pesquisa decente sobre o estado da arte. Um
        dos pontos difíceis seria a marcação dos escopos, mas isso já é implementado pelo núcleo do
        editor Sublime Text, assim provado como possível de ser feito.

        Inicialmente devido a limitação de tempo em 1 ano e meio para um TCC, podemos pensar somente
        um núcleo básico, simples, reutilizável e que talvez possa ajudar no contexto da linguagem
        que vocês desenvolvem.

    O número de recursos/funcionalidades e estratégias de otimizações para serem implementadas, e
    etc, são imensas. Mas esses trabalhos podem ser muito mais para frente depois da entrega do TCC.
    Hoje o controle de espaços em chamadas de funções, declarações de classes, comentários e etc,
    são mais tranquilos de se entender e pensar. Entretanto no requisito e ajuste de indentação,
    inserção/remoção de parenteses redundantes, etc ainda falta estudo sobre como deve ser
    implementado isso.

    Contudo essa especificação por parte do usuário é limitado a linguagens Livres de Contexto
    (máquinas de pilha). Assim caso as especificações de escope precisarem ser feitas em termos de
    linguagens Sensíveis ao Contexto ou ainda Recursivamente Enumeráveis, vai ser preciso tratar
    esses elementos diretamente em C++ (máquina de turing).

    Entretanto não consegue-se pensar facilmente em casos em que precise mais do que tratadores
    Livres de Contexto para realizar a especificação de quais partes do código deve ser necessário
    formatar. Sublime Text faz uso dessa técnica para o Highlight dos códigos das mais diversas
    linguagens e acredita-se que tenha um bom resultado.

\subsection{Research Methods}

@@

@@

@@

>>>>

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{Object Beautifier}\label{sec:software_implementation}

@@

        \item Write the program in C++ for greater performance, allowing the
        formating/beautifying to be dynamic, i.e.,
        as you type the text,
        the text is formatted for you dynamically.
        So on,
        you can focus more on writing code,
        rather than worrying about spacing,
        alignment, parenthesis control, new lines, and whatsoever else.

        \item Use the `doctest' Framework for writing Unit Tests. Because,
        after searching and testing some frameworks for unit testing in C ++,
        this one was entered as serving very well the project requirements.
        As it causes a very low increment in compile time and allows the tests to be written to the same file where the
        program code is found,
        without including them into the final software.

        \item Using a multi-core version of the algorithm,
        then each one of the rules can be processed in parallel over the same original source code.
        This is a quite complex to write because the rules can easily generate conflicts between them, i.e.,
        over work they are producing.
        To resolve this problem,
        we put each rule to generate a change object which such rule is proposing, i.e.,
        the changes it is working on.
        At the end of the processing of all rules,
        a merging of the generated changes which each rule produced will be created,
        and if two rules wanted to change the same piece a.k.a.
        section of code,
        an exception will be thrown and a Changes\q Handler must be available to resolve this conflict.
        If the Changes\q Handler does not exist at the moment for the existing conflict,
        both changes are discarded and only changes without conflict are reflected, i.e.,
        incorporated into the code.

@@

@@

    The advantage of this approach is that we do not need to be aware of the syntax of programming languages that will
    parse.
    This is because we will treat them as common text,
    and it will be the end user that will configure the transformations that will be applied in the text,
    giving freedom to easily configure several programming languages,
    taking advantage of the fact that many of them share similar but not identical structures.

@@

    \item \citeonline{aPrettyGoodFormatting}

@@

    There is a great number of features and optimizations strategies to be implemented.
    But these improvements can be integrated further after the basic toolset implemented on this work.
    Nowadays,
    the control of spaces in function calls,
    class declarations, comments and etc,
    are more easily to understand and think.
    However,
    there is currently a lack of study on how should be implemented,
    features like text and source code indentation adjustment,
    insertion and removal of redundant parenthesis, and such others.

    However,
    the user scope definitions (of languages) are restricted to Context Free languages (powered by stack machines).
    Therefore,
    if the scope specifications need to be made in terms of Context Sensitive or Recursively Enumerable languages,
    it will be necessary to treat these elements directly in the program coding (Turing Machine),
    instead of by user configuration files.

    Moreover,
    you can not easily think of cases where you need more than Free Context handlers to set which parts of the code you
    would like to work on.
    For reference,
    the Sublime Text Editor uniquely uses this approach to perform source code highlight in most diverse languages,
    and has showed to fulfill it purpose.
    TODO put reference to this.
